Notebook of learning from ensemble labels

### 2021-05-13 docs/notebook_learn_dl_ensemble.Rmd

### Single model
Before any tests related to strategies to deal with noisy labels, we will build up a baseline model only using "pure" labels generated by human checking.

@@

#### Baseline

- Unet

@@

  - Scheduler: we decided to use a compose scheduler to have dynamic learning rate. Even though Adam-based optimizer uses dynamic learning rate already, but experiments prove that using both dynamic learning rate and Adam together could have better performance. So we chose to use 0.001 for the first 30 epochs, to use a decayed cyclic scheduler (0.0008 - 0.0012) for epoch 30 - 120, and use another decayed cyclic scheduler (0.0004 - 0.0006) for last 80 epochs.

### Double model

>>>>

### Start up (Baseline)

Before any tests related to strategies to deal with noisy labels, we will build up a baseline model only using "pure" labels generated by human checking.

@@

##### Unet

@@

- Scheduler: we decided to use a compose scheduler to have dynamic learning rate. Even though Adam-based optimizer uses dynamic learning rate already, but experiments prove that using both dynamic learning rate and Adam-based optimizer together could have better performance. So we chose to use 0.001 for the first 30 epochs, to use a decayed cyclic scheduler (0.0008 - 0.0012) for epoch 30 - 120, and use another decayed cyclic scheduler (0.0004 - 0.0006) for last 80 epochs.

###### DeepLab

  [TO BE CONTINUE]

### Resume

#### Single model

#### Double model
